Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2015-01-07 doc/slides/hong+eisner.TLT13.slides.tex
small edits
Fixed some of Jason's minor comments of the slides.

\frame{\frametitle{What We Want:}
  \begin{figure}
    \begin{dependency}
	  \begin{deptext}
	    - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	    the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  \end{deptext}
	  \depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	  \depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	  \depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	  \depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	  \depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	  \depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	  \deproot[edge above, thick, edge style = {red}]{2}{W}
	  \deproot[edge above, thick, edge style = {red}]{7}{WV}
	  \deproot[edge above, thick, edge style = {red}]{10}{X}
	  \depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	  \depedge[edge above, thick, edge style = {red}]{6}{5}{E}
    \end{dependency}
    \caption*{Multiheaded parse with directionalized edges}
  \end{figure}

@@

\frame{\frametitle{Why We Want That}
  \begin{itemize}
    \item We want to develop parsing algorithms for parses that look like this
    \item We couldn't figure out where to get the data to test them.
  \end{itemize}
}

@@

\frame{\frametitle{Link Grammars}
  \begin{itemize}
  \item[] Grammar-based formalism for projective dependency parsing with undirected links
  \item[] Orignal formalism and English Link Grammar created by Davy Temperley, Daniel Sleator, and John Lafferty (1991)
  \end{itemize}
}

\subsection{Link Grammars Intro}
\frame{\frametitle{Link Grammars: How They Work}
  \includegraphics[width=\linewidth]{linkgrammar_example1.png}\footnote{These figures were clipped from the orginal Link Grammar paper: \\``Parsing English with a Link Grammar'' by Sleator and Temperley}
}

@@

  \caption*{Top half is CoNLL. Bottom half is the directionalized link parse.}
\end{figure}

@@

\subsection{What is ILP?}
\frame{\frametitle{What is Integer Linear Programming?}
\begin{itemize}
  \item Its an optimization problem where some or all of the variables are integers. 
  \item The objective function and constraints are linear.
  \item Its NP-Hard! But good solvers exist that work well most of the time.
  \item Our ILP is encoded as a ZIMPL program and solved using the SCIP Optimization Suite\footnote{\url{http://scip.zib.de/}} 
\end{itemize}
}

@@

\frame{\frametitle{ILP Results: Top 25 Most Occuring Labels}

>>>>

\frame{\frametitle{What We Wanted:}
  \begin{figure}
    \begin{dependency}
	  \begin{deptext}
	    - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	    the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  \end{deptext}
	  \depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	  \depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	  \depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	  \depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	  \depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	  \depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	  \deproot[edge above, thick, edge style = {red}]{2}{W}
	  \deproot[edge above, thick, edge style = {red}]{7}{WV}
	  \deproot[edge above, thick, edge style = {red}]{10}{X}
	  \depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	  \depedge[edge above, thick, edge style = {red}]{6}{5}{E}
    \end{dependency}
    \caption*{Multiheaded parse with directionalized edges}
  \end{figure}

@@

\frame{\frametitle{Why We Wanted That}
  \begin{itemize}
    \item We want to develop parsing algorithms for parses that look like this
    \item We couldn't figure out where to get the data to test them.
  \end{itemize}
}

@@

\frame{\frametitle{Link Grammars}
  \begin{itemize}
  \item[] Grammar-based formalism for projective dependency parsing with undirected links
  \item[] Original formalism and English Link Grammar created by Davy Temperley, Daniel Sleator, and John Lafferty (1991)
  \end{itemize}
}

\subsection{Link Grammars Intro}
\frame{\frametitle{Link Grammars: How They Work}
  \includegraphics[width=\linewidth]{linkgrammar_example1.png}\footnote{These figures were clipped from the original Link Grammar paper: \\``Parsing English with a Link Grammar'' by Sleator and Temperley}
}

@@

  \caption*{Bottom half is CoNLL. Top half is the directionalized link parse.}
\end{figure}

@@

\subsection{What is ILP?}
\frame{\frametitle{What is Integer Linear Programming?}
\begin{itemize}
  \item An optimization problem where some or all of the variables are integers. 
  \item The objective function and constraints are linear.
  \item In general, it's NP-Hard! But good solvers exist that work well most of the time.
  \item Our ILP is encoded as a ZIMPL program and solved using the SCIP Optimization Suite\footnote{\url{http://scip.zib.de/}} 
\end{itemize}
}

@@

\frame{\frametitle{ILP Results: Top 25 Most Occurring Labels}
